\textbf{COMP0085 Summative Assignment}

### 2023-01-02 submission.tex
update gamma prior parameters for vb
update plots
refactor folder structure for models

\newpage
The Python code for the binary latent factor model:
\lstinputlisting[language=Python]{src/models/binary_latent_factor_model.py}

\newpage
The Python code for an abstract binary latent factor model approximation:
\lstinputlisting[language=Python]{src/models/binary_latent_factor_model_approximation.py}

\newpage
The Python code for mean field learning:
\lstinputlisting[language=Python]{src/models/mean_field_approximation.py}

@@

\newpage
\begin{figure}[h]
\centering
\begin{minipage}{.6\textwidth}
  \centering
\includegraphics[scale=0.15]{outputs/q4/b-latent-factors}
\caption{Learned Latent Factors}
\label{fig:}
\end{minipage}%
\begin{minipage}{.2\textwidth}
  \centering
\includegraphics[scale=0.11]{outputs/q4/b-alpha-trained}
\caption{Alpha values}
\label{fig:}
\end{minipage}
\end{figure}

@@

\newpage
The Python code for Variational Bayes:
\lstinputlisting[language=Python]{src/models/variational_bayes.py}

@@

\newpage
The Python code for the Boltzmann machine:
\lstinputlisting[language=Python]{src/models/boltzmann_machine.py}

\newpage
The Python code for message passing:
\lstinputlisting[language=Python]{src/models/message_passing.py}

@@

\newpage
\section*{Appendix 1: constants.py}
\lstinputlisting[language=Python]{src/constants.py}
\newpage
\section*{Appendix 2: main.py}
\lstinputlisting[language=Python]{main.py}
\newpage
\section*{Appendix 3: generate\_images.py}
\lstinputlisting[language=Python]{src/generate_images.py}
\newpage
\section*{Appendix 4: MStep.py}
\lstinputlisting[language=Python]{demo_code/MStep.py}
\end{document}

>>>>

\newpage
The Python code for the binary latent factor model:
\lstinputlisting[language=Python]{src/models/binary_latent_factor_models/binary_latent_factor_model.py}

\newpage
The Python code for mean field learning:
\lstinputlisting[language=Python]{src/models/binary_latent_factor_approximations/mean_field_approximation.py}

@@

\newpage
\begin{figure}[h]
\centering
\includegraphics[scale=0.47]{outputs/q4/b-1-latent-factors-comparison}
\caption{Learned Latent Factors vs Inverse Alpha}
\label{fig:}
\end{figure}

\newpage
\begin{figure}[h]
\centering
\includegraphics[scale=0.47]{outputs/q4/b-2-latent-factors-comparison}
\caption{Learned Latent Factors vs Inverse Alpha}
\label{fig:}
\end{figure}

@@

\newpage
The Python code for Variational Bayes:
\lstinputlisting[language=Python]{src/models/binary_latent_factor_models/variational_bayes.py}

@@

\newpage
The Python code for the Boltzmann machine:
\lstinputlisting[language=Python]{src/models/binary_latent_factor_models/boltzmann_machine.py}

\newpage
The Python code for message passing:
\lstinputlisting[language=Python]{src/models/binary_latent_factor_approximations/message_passing.py}

@@

\newpage
\section*{Appendix 1: abstract\_binary\_latent\_factor\_model.py}
\lstinputlisting[language=Python]{src/models/binary_latent_factor_models/abstract_binary_latent_factor_model.py}

\newpage
\section*{Appendix 2: abstract\_binary\_latent\_factor\_approximation.py}
\lstinputlisting[language=Python]{src/models/binary_latent_factor_approximations/abstract_binary_latent_factor_approximation.py}

\newpage
\section*{Appendix 3: main.py}
\lstinputlisting[language=Python]{main.py}

\newpage
\section*{Appendix 4: constants.py}
\lstinputlisting[language=Python]{src/constants.py}

\newpage
\section*{Appendix 5: generate\_images.py}
\lstinputlisting[language=Python]{src/generate_images.py}
\newpage
\section*{Appendix 6: MStep.py}
\lstinputlisting[language=Python]{demo_code/MStep.py}
\end{document}
